Fourmile-Best Runs

### 2025-12-14 fourmile_output_dec2024.Rmd
met shifts

setwd('/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates')

@@

setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/cals")

@@

write_csv(params, '/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/params_unburn.csv')

@@

ggplot(params_combo, aes(x=burn, y=value, fill=input_data)) +
  geom_boxplot() +
  facet_wrap(~param, scales = 'free_y')
# 
#write_csv(params_combo, '/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/params_burn_unburn.csv')

@@

#write_csv(params_weighted, '/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/params_weighted_dec2024.csv')

@@

#write_csv(nseCats, '/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/nseCats.csv')

@@

# write_csv(flow_plot,
#           '/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/all_kge.csv')

@@

#write_csv(pbiasCats, '/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/pbiasCats.csv')

@@

gw_gridall <- read_csv(here('38HRU_dec2024_updates/catchment_output/grid_all.csv'), skip = 3) %>%
  slice(-c(1,2)) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'grid_all') %>%
  mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))

gw_statnall <- read_csv(here('38HRU_dec2024_updates/catchment_output/statn_all.csv'), skip = 3) %>%
  slice(-c(1,2)) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'statn_all') %>%
  mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))

@@

gw <- bind_rows(
  gw_gridall, gw_statnall
  # gw_grid2011, gw_grid2012,
  # gw_grid2013, gw_grid2014,
  # gw_grid2015, gw_grid2016,
  # gw_grid2017, gw_grid2018,
  # gw_grid2019, gw_grid2020,
  # gw_statn2011, gw_statn2012,
  # gw_statn2013, gw_statn2014,
  # gw_statn2015, gw_statn2016,
  # gw_statn2017, gw_statn2018,
  # gw_statn2019, gw_statn2020
) %>%
  mutate(date = mdy(time),
         year = year(date)) %>%
  arrange(date)

>>>>

setwd('/Users/megansears/Documents/Repos/fourmile/38HRU_oct2025_updates')

@@

setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_oct2025_updates/cals")

@@

write_csv(params, '/Users/megansears/Documents/Repos/fourmile/38HRU_oct2025_updates/params_unburn.csv')

@@

ggplot(params_combo, aes(x=burn, y=value, fill=input_data)) +
  geom_boxplot() +
  facet_wrap(~param, scales = 'free_y')
# 
write_csv(params_combo, '/Users/megansears/Documents/Repos/fourmile/38HRU_oct2025_updates/params_burn_unburn.csv')

@@

write_csv(params_weighted, '/Users/megansears/Documents/Repos/fourmile/38HRU_oct2025_updates/params_weighted_oct2025.csv')

@@

write_csv(nseCats, '/Users/megansears/Documents/Repos/fourmile/38HRU_oct2025_updates/nseCats.csv')

@@

write_csv(flow_plot,
          '/Users/megansears/Documents/Repos/fourmile/38HRU_oct2025_updates/all_kge.csv')

@@

write_csv(pbiasCats, '/Users/megansears/Documents/Repos/fourmile/38HRU_oct2025_updates/pbiasCats.csv')

@@

gw_gridall <- read_csv(here('38HRU_oct2025_updates/catchment_output/grid_all.csv'), skip = 3) %>%
  slice(-c(1,2)) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'grid_all') %>%
  mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))

gw_statnall <- read_csv(here('38HRU_oct2025_updates/catchment_output/statn_all.csv'), skip = 3) %>%
  slice(-c(1,2)) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'statn_all') %>%
  mutate(across(c(catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w), as.numeric))

@@

gw <- bind_rows(
  gw_gridall, gw_statnall
  # gw_grid2011, gw_grid2012,
  # gw_grid2013, gw_grid2014,
  # gw_grid2015, gw_grid2016,
  # gw_grid2017, gw_grid2018,
  # gw_grid2019, gw_grid2020,
  # gw_statn2011, gw_statn2012,
  # gw_statn2013, gw_statn2014,
  # gw_statn2015, gw_statn2016,
  # gw_statn2017, gw_statn2018,
  # gw_statn2019, gw_statn2020
) %>%
  mutate(date = ymd(time),
         year = year(date)) %>%
  arrange(date)

### 2025-12-14 highestKGE_models.Rmd
met shifts

>>>>

# Performance
Above is old

flow <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_oct2025_updates/discharge_table2.csv') %>%
  filter(!obs == -9999) %>%
  summarize(KGE_grid19_statnin = KGE(obs, grid2019_statninput),
            KGE_statnall_gridin = KGE(obs, statnall_gridinput),
            pbias_grid19_statnin = pbias(obs, grid2019_statninput),
            pbias_statnall_gridin = pbias(obs, statnall_gridinput),
            NSE_grid19_statnin = NSE(obs, grid2019_statninput),
            NSE_statnall_gridin = NSE(obs, statnall_gridinput),
            )

flow
